\begin{summary}
 
The aim of this project is to develop a market research system and show how to employ big data analytics and online methods to generate affordable and high-quality data-driven marketing insights using non stationary data sets. Other such applications exist but they solve very specific business problems or require field specific knowledge. The proposed system aims at removing all the guesswork and provide automatically an array of high quality marketing information. 
  
\keywords{Marketing Research, Big Data, Machine Learning, Kernel Machines}
  
\end{summary}

\begin{dedication}
	
I lovingly dedicate my dissertation work to my family and to the friends that have helped and supported me during the difficult times that ensued as a result of the COVID-19 pandemic.
  
\end{dedication}

\begin{acknowledgements}
	
I would like to extend my heartiest thanks to all those who helped and guided me during my training period. I would like to thank my supervisor, professor Stylianos Sygletos. His guidance and help have been very helpful in putting the project on the right track and resolve some issues that occurred along the way. I would like to give a special thanks to Kety Mayelin Jimenez Tejeda and her family for their hospitality and support. A special thanks goes also to Angela Onaney Sanchez De La Cruz for the beautiful moments we shared together. Last but not least, I would like to thank my family for their presence and unconditional love.

\end{acknowledgements}

