\newpage
\chapter{Glossary}


\paragraph{C}
\noindent\rule{16cm}{0.4pt}

\subparagraph{Continuous Integration and Continuous Delivery}
Continuous Integration and Continuous Delivery are the processes in which a development team integrates changes frequently into the main branch while ensuring that it does not impact any changes made previously or by other developers.

\subparagraph{Customer}
It is the person with the highest stakes in the project and understands both the business needs and operational constraints of the project. He guides the development on and knows the priorities that should be emphasized.

\paragraph{D}

\noindent\rule{16cm}{0.4pt}

\subparagraph{Data Analysis}
It is the process of collecting, transforming, cleaning, and modelling data with the goal of discovering information.

\subparagraph{Data Warehouse}
It is a large centralized repository of data that transform all multiple data formats into a single format and consolidate them in one place. 

\subparagraph{Data Mart}
This is a a data warehouse oriented to specific business lines. It contains repositories of summarized data collected for analysis of a specific section or unit within an organization. 

\subparagraph{Descriptive Analytics}
It is the interpretation of historical data to better understand changes that have occurred in a business. Descriptive analytics describes the use of a range of historic data to draw comparisons. Most commonly reported financial metrics are a product of descriptive analytics, for example, year-over-year pricing changes, month-over-month sales growth, the number of users, or the total revenue per subscriber. These measures all describe what has occurred in a business during a set period.

\subparagraph{Development Methodology}
This is the approach chosen to manage the different phases of the life cycle of an engineering project. The most common models are Waterfall, Agile, Lean, Iterative, Prototyping, DevOps, Spiral or V-model. It includes phases for tracing the progress of a product from a planned idea to its final release into operation and maintenance. 

\paragraph{M}

\noindent\rule{16cm}{0.4pt}

\subparagraph{Marketing Research}
It is the systematic design, collection, analysis, and reporting of data of the market of a company. Market-related data such as sales data, advertising expenditure, customer information, etc.is thus recorded over time.


\paragraph{P}
\noindent\rule{16cm}{0.4pt}

\subparagraph{Minimum Viable Product}
A minimum viable product, or MVP, is a product with enough features to attract early-adopter customers and validate a product idea early in the product development cycle. In industries such as software, the MVP can help the product team receive user feedback as quickly as possible to iterate and improve the product.

\paragraph{S}
\noindent\rule{16cm}{0.4pt}

\subparagraph{Stakeholder}
A stakeholder is a party that has an interest in a company and can either affect or be affected by the business. The primary stakeholders in a typical corporation are its investors, employees, customers, and suppliers.




















